---
title: "Individual Project 3"
author: "Jie Zhou"
date: ""
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)
```

```{r source}
#source("constants.R")
#source("functions.R")
library(data.table)
library(DT)
library(ggplot2)
library(dplyr)
```

```{r constants}
```

```{r functions}

```

```{r read_data}
data=fread("mobile phone survey data.csv")
```


# Report {.tabset}

## Part 1:  Summary


```{r part1}
head(data)
cbind("Number of Products"=length(unique(data$Product)),"Number of respondents"=length(unique(data$id)))
```

This dataset contains 10,000 survey respondents, 20 products asked, and 3 various types of information, including
      
      "Demographic information" of survey respondents:
                 age, gender, income, region, persona, and the specific product they purchased,
                 
      "Product engagement" of respondents:  
                whether aware of the product , whether considering buying the product, whether they consume the 
                product, the satisfaction level (0-10), and whether advocating the product, 
                
      and "Product/brand perception" of respondents:
       user friendliness, fast, battery life, camera, sleek, stylish, status symbol, screen size, boring, bulky, 
       fragile,and expensive. Their ratings about products are stored in the range of 0 (bad)-10 (good).
       
To do the further analysis, consultants are able to divide data into various segments based on the demographic information, like region and persona, and determine which product has the best performance by various types of ratings, the significant relationship between respondents' demographic information and their ratings, and how many respondents who are aware of this product have not purchased.


## Part 2:  Specific Questions {.tabset}


### Q1: Resopendent Variables {.tabset}

#### Age Group

```{r q1_age.group}
data[Age>=18&Age<35,age_group:="18-35"]
data[Age>=35&Age<50,age_group:="35-50"]
data[Age>=50&Age<65,age_group:="50-65"]
data[Age>=65,age_group:="65+"]

unique_age_group <- unique(data[,age_group,by="id"])
datatable(unique_age_group[,.("Percentage of Respondents"=paste0(100*.N/nrow(unique_age_group),"%")),keyby="age_group"])
```

#### Gender

```{r q1_gender}
unique_gender <- unique(data[,Gender,by="id"])
datatable(unique_gender[,.("Percentage of Respondents"=paste0(100*.N/nrow(unique_gender),"%")),keyby="Gender"])
```

#### Income Group

```{r q1_income.group}
#define income group
data[Income<50000,"Income Group":="<$50,000"]
data[Income>=50000&Income<75000,"Income Group":="$50,000-75,000"]
data[Income>=75000&Income<100000,"Income Group":="$75,000-100,000"]
data[Income>=100000&Income<150000,"Income Group":="$100,000-150,000"]
data[Income>=150000,"Income Group":=">$150,000"]

unique_income_group <- unique(data[,`Income Group`,keyby="id"])
order=c("<$50,000","$50,000-75,000","$75,000-100,000","$100,000-150,000",">$150,000")
q1_income.group <- unique_income_group[,.("Percentage of Respondents"=paste0(100*.N/nrow(unique_income_group),"%")),keyby=`Income Group`]
datatable(q1_income.group)
```

#### Region
 
```{r region}
unique_region <- unique(data[,Region,keyby="id"])
datatable(unique_region[,.("Percentage of Respondents"=paste0(100*.N/nrow(unique_region),"%")),keyby="Region"])
```

#### Persona

```{r persona}
unique_persona <- unique(data[,Persona,keyby="id"])
datatable(unique_persona[,.("Percentage of Respondents"=paste0(100*.N/nrow(unique_persona),"%")),keyby="Persona"])
```


### Q2:  Segmented Outcomes {.tabset}

#### Part A

What are the top 5 products by Awareness rates in the Northeast?

```{r q2_a}
datatable(data[Region=="Northeast",.("Awareness Score"=paste(round(100*sum(Awareness)/.N,2),"%")),keyby="Product"][order(-`Awareness Score`),.SD[1:5]])

```

#### Part B

What are the top 5 products by Advocacy rates among females who earn at least $100,000?

```{r q2_b}

data[Income>=100000&Gender=="Female",.("Advocacy Score" = round(100*mean(Advocacy, na.rm=T)/max(Advocacy, na.rm = T),2)), by = "Product"][order(-`Advocacy Score`),.SD[1:5]]

```





### Q3:  Overall Brand Perceptions {.tabset}

What are the top 5 brands by the overall average perception?


```{r q3}
q3 <- data[,c(7,9:20)]


q3_positive_perception <- q3[,lapply(.SD,function(x)mean(x,na.rm = T)),keyby="Product",.SDcols=names(q3[,2:9])]# scores for postive perceptions

q3_negative_perception <- q3[,lapply(.SD,function(x)mean(x,na.rm = T)),keyby="Product",.SDcols=names(q3[,10:13])]# scores for negative perceptions
q3_negative_perception[,2:5] <- 10-q3_negative_perception[,2:5] # invert negative perception

q3_perception_aggregate <- merge(q3_positive_perception,q3_negative_perception)

datatable(q3_perception_aggregate[,.("Overall Average Perception"=round(rowMeans(.SD),4)),keyby="Product"][order(-`Overall Average Perception`),.SD[1:5]])
```


### Q4: Gaps in Outcomes {.tabset}


#### Part A

Which 5 products have the largest gap between the rate of consumption and the rate of awareness?

```{r q4_a}

aware_rate <- data[,.("Rate of Awareness"=mean(Awareness)),keyby="Product"]

consum_rate <-data[,.("Rate of Consumption"=mean(Consumption,na.rm=T)),keyby="Product"]

q4_a <- merge(aware_rate,consum_rate)

top_5_a <- q4_a[,.(Product,"Gap between Awareness and Consumption"=round(100*abs(`Rate of Consumption`-`Rate of Awareness`),2))][order(-`Gap between Awareness and Consumption`),.SD[1:5]]

ggplot(top_5_a,aes(reorder(Product,-`Gap between Awareness and Consumption`),`Gap between Awareness and Consumption`,label =`Gap between Awareness and Consumption`))+geom_bar(stat="identity",fill="#f68060")+xlab("Product")+ylab("Difference between Awareness and Consumption (%)")+geom_text(aes(label =paste0(`Gap between Awareness and Consumption`,"%")),vjust=-0.5)

```

#### Part B

Which 5 products have the largest gap between the rate of Awareness and the average Satisfaction?

```{r q4_b}
satis_rate <- data[,.(`Average Satisfaction`=mean(Satisfaction,na.rm = T)),keyby="Product"]
q4_b <- merge(aware_rate,satis_rate)

q4_b[,.(Product,"Gap between Awareness and Satisfaction"=round(abs(100*`Rate of Awareness`-10*`Average Satisfaction`),2))][order(-`Gap between Awareness and Satisfaction`),.SD[1:5]]%>%
   ggplot(aes(reorder(Product,-`Gap between Awareness and Satisfaction`),`Gap between Awareness and Satisfaction`,label =`Gap between Awareness and Satisfaction`))+geom_bar(stat="identity",fill="blue")+xlab("Product")+ylab("Difference between Awareness and Satisfaction (%)")+geom_text(aes(label =`Gap between Awareness and Satisfaction`),vjust=-0.5)
```


### Q5: Aggregated Engagement {.tabset}

#### Part A

How much impact does respondent's overall trends in awareness have for that person's awareness with Buzzdial phones?

```{r q5_a}
aggregated_engagement <- data[Product!="Buzzdial",.(aggregated_engagement=ifelse(sum(Awareness,na.rm = T)==0, 0, mean(Awareness,na.rm = T))),by="id"]

q5_a <-merge(data,aggregated_engagement)[Product=="Buzzdial"]
model_q5_a<- glm(Awareness~age_group+Gender+`Income Group`+aggregated_engagement+Region+Persona,q5_a,family=binomial)

#aggregate table 
datatable(cbind(round(exp(cbind("Odds ratio" = model_q5_a$coefficients, confint(model_q5_a, level = 0.95))),4),"P values"=round(coef(summary(model_q5_a))[,'Pr(>|z|)'],4)))

```

#### Part B

How much impact does respondent's overall trends in satisfaction have for that person's satisfaction with Buzzdial phones?

```{r q5_b}
# calculate aggregated engagement of satisfaction
aggregated_satisfaction <- data[Product!="Buzzdial",.(aggregated_engagement=ifelse(sum(Satisfaction,na.rm = T)==0, 0, mean(Satisfaction,na.rm = T)/10)),by="id"]
# merge data
q5_b <-merge(data,aggregated_satisfaction)[Product=="Buzzdial"]
# build model
model_q5_b <- lm(Awareness~age_group+Gender+`Income Group`+aggregated_engagement+Region+Persona,q5_b)


table_b <- cbind("Coefficients"=round(model_q5_b$coefficients,4), round(confint(model_q5_b,level = 0.95),4),"P values"=round(coef(summary(model_q5_b))[,4],4))
DT::datatable(table_b)

```

